---
title: "Cases in all of Germany"
author: "Nancy Yu"
date: "2021-11-17T21:00:00+01:00"
categories: ["R visualization"]
tags: ["covid19"] 

---


```{r setup, include=F, message=F}

# setwd('/Users/nancyyu/Documents/R website/First_Website/')
knitr::opts_chunk$set(echo=TRUE, collapse = TRUE)

libload<-function(...) {
    libs<-unlist(list(...))
    req<-unlist(lapply(libs,require,character.only=TRUE))
    need<-libs[req==FALSE]
    if(length(need)>0){ 
        install.packages(need, repos = "https://ftp.fau.de/cran/")
        lapply(need, require, character.only=TRUE)
    }
}
packages <- c("data.table", "ggplot2", "dplyr", "stats", "RColorBrewer", "readr", "here", "scales")
libload(packages)


`%notin%` <- function(x,y) !(x %in% y) 
all.cases <- read_csv(here("static", "data", "GermanyAllNumbers.csv"))
all.cases$dates <- as.Date(all.cases$date)

color_deu <- '#0000FF'

colors16 <- c('#A6CEE3', '#1F78B4', '#B2DF8A', '#33A02C',
              '#000000', '#FF7F00', '#CAB2D6', 
              '#EFBE2F', '#FFFF99', '#B15928', '#F3A3B1', '#466D32',
              '#621AC1', '#C7D7D0', '#E31A1C','#F20CF4', '#123456')

```


*Last modified: 2021-11-17.*  


*Data source: [Our World In Data]*

[Our World In Data]: https://ourworldindata.org/coronavirus

_**December 2, 2020**_: Our World In Data originally obtained their data from ECDC. They have since switched data source to John Hopkins, and the daily numbers looked different from ECDC/RKI, due to different ways of updating their data. Therefore I have switched data source to [RKI] which seems to be the primary source for ECDC. 


[RKI]: https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Fallzahlen.html


##### Cumulative number of confirmed SARS-CoV-2 cases in Germany in linear scale since March 15, 2020

```{r cum_linear_all, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi = 96}

# Plot 1 == Linear scale for total number of cases
cum.plot <- ggplot(data=all.cases, aes(x=date, y=total_cases)) +
            geom_line(color=color_deu) + geom_point(size = 0.2) +     
          #  scale_color_brewer(palette = 'Paired') + 
          #  scale_colour_manual(name= "State", values= colors16) +
          #  scale_x_continuous('Days since the 100th case', limits=c(0,200)) + 
            scale_x_date(name='Date', labels=date_format('%Y-%m-%d')) + 
            scale_y_continuous(name="Total cases", labels= comma) + 
            #ggtitle('Linear scale') +
            theme_minimal() + theme(axis.text.x = element_text(angle=20, hjust=0.5, vjust=0.5))

print(cum.plot) 

```
<br/>
<br/>
  
##### Number of confirmed new cases in Germany since March 15, 2020

This plot shows the increase in the number of confirmed new cases. Each data point is averaged over 7 previous consecutive days . Note: This is not necessarily reflective in the increase of *actual* number of cases each day, since the number of tests for the virus has been increasing as the pandemic progressed.

_**December 28, 2020**: Note that during the Christmas holidays the numbers are artificially low as there are fewer tests conducted, fewer people go get tested, and also the reporting of numbers are delayed._


```{r new_cases7days_all, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}

newcase7.plot <- ggplot(data=all.cases, aes(x=date, y=new_cases_smoothed)) +
            geom_line(color=color_deu) + geom_point(size = 0.2) + 
       #     scale_color_brewer(palette = 'Paired') +
      #      scale_colour_manual(name= "State", values= colors16) +
            scale_x_date(name='Date', labels=date_format('%Y-%m-%d')) + 
            scale_y_continuous(name="Number of new cases (averaged over 7 days)") + 
            #ggtitle('Linear scale') +
            theme_minimal() + theme(axis.text.x = element_text(angle=20, hjust=0.5, vjust=0.5))

print(newcase7.plot)
 
```


<br/>
<br/>
<br/>

##### Cumulative number of deaths since March 15, 2020 

```{r cum_deaths_all, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}
#num.deaths <- read_csv(here("static", "data", "GermanyTotalDeaths10States.csv"))

# Choose all the data points for the selected countries starting from Days_5 > 0
#deaths.final <- states.final[states.final$DeathsDays_5 > 0,]

# Plot 1 == Linear scale for total number of cases
deaths.plot <- ggplot(data= all.cases, aes(x=dates, y=total_deaths)) +
   geom_line(color=color_deu) + geom_point(size = 0.2) + 
  # scale_color_brewer(palette = 'Paired') +
#   scale_colour_manual(name= "State", values= colors16) +
#   scale_x_continuous('Days since 5 deaths', limits=c(0,200)) + 
    scale_x_date(name='Date', labels=date_format('%Y-%m-%d')) + 
    scale_y_continuous(name="Total deaths") + 
#   scale_y_continuous("Total deaths", trans = 'log10', breaks = logbreaks, 
#                      minor_breaks = logminor_breaks) +
#   annotation_logticks(sides="l") + 
   #ggtitle('Linear scale') +
   theme_minimal() +
  theme(axis.text.x = element_text(angle=20, hjust=0.5, vjust=0.5))

print(deaths.plot)

```

<br/>
<br/>
<br/>

##### Number of confirmed new deaths since March 15,2020

This plot shows the increase in the number of confirmed deaths. Each data point is averaged over past 7 consecutive days.


```{r deaths_7days_all, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}
#new.cases <- read_csv(here("static", "data", "GermanyNewCases10States.csv"))

#states.final$Dates <- as.Date(states.final$Dates)
#death7days <- states.final
#death7days <- death7days[death7days$Dates > as.Date('2020-03-20'),]

death7days.plot <- ggplot(data= all.cases, aes(x=date, y=new_deaths_smoothed)) +
            geom_line(color=color_deu) + geom_point(size = 0.2) + 
       #     scale_color_brewer(palette = 'Paired') +
            scale_colour_manual(values= color_deu) +
            scale_x_date(name='Date', labels=date_format('%Y-%m-%d')) + 
            scale_y_continuous(name="Number of new deaths (averaged over 7 days)", limits=c(0,900)) + 
           
            #ggtitle('Linear scale') +
            theme_minimal() + theme(axis.text.x = element_text(angle=20, hjust=0.5, vjust=0.5))

print(death7days.plot)
 
```
<br/>
<br/>
<br/>






