---
title: "Tracking the coronavirus outbreak in Germany from March to June 2020"
author: "Nancy Yu"
date: "2020-08-12T8:00:00-02:00"
categories: ["R visualization"]
tags: ["covid19"]

---


```{r setup, include=F, message=F}

knitr::opts_chunk$set(echo=TRUE, collapse = TRUE)

libload<-function(...) {
    libs<-unlist(list(...))
    req<-unlist(lapply(libs,require,character.only=TRUE))
    need<-libs[req==FALSE]
    if(length(need)>0){ 
        install.packages(need, repos = "https://ftp.fau.de/cran/")
        lapply(need, require, character.only=TRUE)
    }
}
packages <- c("data.table", "ggplot2", "dplyr", "stats", "RColorBrewer", "readr", "here", "scales")
libload(packages)


`%notin%` <- function(x,y) !(x %in% y) 
cumulative.cases <- read_csv(here("static", "data", "Germany10States.csv"))
germany.16states <- read_csv(here("static", "data", "Germany16States.csv"))

colors16 <- c('#A6CEE3', '#1F78B4', '#B2DF8A', '#33A02C',
              '#000000', '#FF7F00', '#CAB2D6', 
              '#EFBE2F', '#FFFF99', '#B15928', '#F3A3B1', '#466D32',
              '#621AC1', '#C7D7D0', '#E31A1C','#F20CF4', '#123456')

```

*Last modified: 2020-08-12.*  

_**May 9, 2020**: Added data for all 16 states for all graphs._


This is my attempt to visualize some SARS-CoV-2 data with some R code (please pardon the non-optimal layout). German data is obtained from the [Robert Koch Institute]. Data used from March 15-June, 2020 (not updated every day).

[Robert Koch Institute]: https://www.rki.de/DE/Content/InfAZ/N/Neuartiges_Coronavirus/Fallzahlen.html

For more extensive information about SARS-CoV-2 in Germany in English, see [here](https://www.german-way.com/for-expats/living-in-germany/expat-how-to-guides-for-germany/coronavirus-in-germany-information/).


<br/>
<br/>

##### Cumulative number of confirmed SARS-CoV-2 cases in Germany in linear scale since 100th case

```{r cum_linear, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi = 96}

## 10 States with the highest cumulative cases ##
#################################################

#states.filter <- cumulative.cases[cumulative.cases$Days_100 > 0,]
#states.sel <- unique(states.filter$State)

# Choose all the data points for the selected countries starting from Days_100 > 0
#states.final <- cumulative.cases[cumulative.cases$Days_100 > 0,]
states.final <- germany.16states[germany.16states$Days_100 > 0,]

# Plot 1 == Linear scale for total number of cases
cum.plot <- ggplot(data=states.final, aes(x=Days_100, y=Total_Cases, group=State, color=State)) +
            geom_line() + geom_point(size = 0.3) +     
          #  scale_color_brewer(palette = 'Paired') + 
            scale_colour_manual(name= "State", values= colors16) +
            scale_x_continuous('Days since the 100th case', limits=c(0,160)) + 
            scale_y_continuous("Total cases") + 
            #ggtitle('Linear scale') +
            theme_minimal()

print(cum.plot) 

```
<br/>
<br/>
  
##### Number of confirmed cases shown in logarithmic scale

For exponential growth, the amount of time cases increase from 100 to 1000 is roughly the same as the amount of time it goes from 1000 to 10000. By showing the numbers in logarithmic plot, we can see that the growth curves are slowly bending downwards, thanks to the social distancing measures. 


```{r cum_logscale, echo = F, message=F, warning=F, fig.width=8, fig.height=5, dpi=96}

## Logarithmic scale ##
#######################

base_breaks <- function(n = 10){
  function(x) {
    axisTicks(log10(range(x, na.rm = TRUE)), log = TRUE, n = n)
  }
}

logbreaks <- 10^(-10:10)
logminor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))

cum.plot2 <- ggplot(data=states.final, aes(x=Days_100, y=Total_Cases, group=State, color=State)) +
             geom_line() + geom_point(size=0.3) + 
          #   scale_color_brewer(palette = 'Paired') +
             scale_colour_manual(name= "State", values= colors16) +
             scale_x_continuous(name='Days since the 100th case', limits=c(0,160)) + 
             scale_y_continuous(name="Total cases", trans = 'log10', breaks = logbreaks, minor_breaks = logminor_breaks) +
             annotation_logticks(sides="l") + 
             #ggtitle('Logarithmic scale') +
             theme_minimal()

print(cum.plot2)

```
<br/>
<br/>
<br/>
  
##### Cumulative number of cases per 100,000 inhabitants

This graph shows the cumulative increase of cases adjusted for the population size of each state.  Per capita, Hamburg's cases are comparable with Bavaria and Baden-Württemburg.

_**May 8, 2020**: added data from all 16 German states for this plot._

```{r cum_per100, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi = 96}

#states16.filter <- germany.16states[germany.16states$Days_100 > 0,]
#states16.sel <- unique(states16.filter$State)

# Choose all the data points for the selected countries starting from Days_100 > 0 
#states16.final <- states16.filter[states16.filter$State %in% states16.sel & states16.filter$Days_100 > 0,]

states16.final <- germany.16states[germany.16states$Days_100 > 0,]

# Plot 1 == Linear scale for total number of cases
per100.plot <- ggplot(data=states16.final, aes(x=Days_100, y=Per100, group=State, color=State)) +
            geom_line() + geom_point(size = 0.3) + 
            # scale_color_brewer(palette = 'Paired') +
            scale_colour_manual(name= "State", values= colors16) +
            scale_x_continuous('Days since 100 cases', limits=c(0,160)) + 
            scale_y_continuous("Cumulative cases per 100,000") + 
            #ggtitle('Linear scale') +
            theme_minimal()

print(per100.plot)

```

_**April 11, 2020**: I had not realized at all how high Saarland's numbers were when normalized for its population._

_**May 19, 2020**: I am not sure what's happening with Bremen. It could be just a data entry error, or maybe it just doesn't have the virus under control at all._ 

<br/>
<br/>
<br/>

  
##### Number of confirmed new cases in Germany by States since March 17, 2020

This plot shows the increase in the number of confirmed new cases. Each data point is averaged over 7 previous consecutive days . Note: This is not necessarily reflective in the increase of *actual* number of cases each day, since the number of tests for the virus has been increasing as the pandemic progressed.

_**April 9, 2020**: The graph doesn't show it (5 day average, later changed to 7 day average), but the numbers seem to be going up again. Hard to say what the trend is until after Easter holidays. Are the tests processed slower during the holidays? We will see next week._ 

_**April 18, 2020**: I really don't like that the number of new cases are creeping back up this week for most of the states._

_**April 22, 2020**: Modified rolling 5 day average to 7 days to smooth out the curves more._

```{r new_cases7days, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}
#new.cases <- read_csv(here("static", "data", "GermanyNewCases10States.csv"))

new7days <- states.final[states.final$Avg_7days > 0,]
new7days$Dates <- as.Date(new7days$Dates)

newcase7.plot <- ggplot(data=new7days, aes(x=Dates, y=Avg_7days, group=State, color=State)) +
            geom_line() + geom_point(size = 0.3) + 
       #     scale_color_brewer(palette = 'Paired') +
            scale_colour_manual(name= "State", values= colors16) +
            scale_x_date(name='Date', labels=date_format('%Y-%m-%d')) + 
            scale_y_continuous(name="Number of new cases (averaged over 7 days)") + 
            #ggtitle('Linear scale') +
            theme_minimal() + theme(axis.text.x = element_text(angle=20, hjust=0.5, vjust=0.5))

print(newcase7.plot)
 
```


<br/>
<br/>
<br/>

##### Cumulative number of deaths in log scale

Data shown since the 5th death.

```{r cum_deaths, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}
#num.deaths <- read_csv(here("static", "data", "GermanyTotalDeaths10States.csv"))

# Choose all the data points for the selected countries starting from Days_5 > 0
deaths.final <- states.final[states.final$DeathsDays_5 > 0,]

# Plot 1 == Linear scale for total number of cases
deaths.plot <- ggplot(data=deaths.final, aes(x=DeathsDays_5, y=Deaths, group=State, color=State)) +
   geom_line() + geom_point(size = 0.3) + 
  # scale_color_brewer(palette = 'Paired') +
   scale_colour_manual(name= "State", values= colors16) +
   scale_x_continuous('Days since 5 deaths', limits=c(0,160)) + 
   scale_y_continuous("Total deaths", trans = 'log10', breaks = logbreaks, 
                      minor_breaks = logminor_breaks) +
   annotation_logticks(sides="l") + 
   #ggtitle('Linear scale') +
   theme_minimal()

print(deaths.plot)

```

<br/>
<br/>
<br/>

##### Cumulated number of deaths per 100,000 inhabitants

*Added May 20, 2020*

This graph shows the cumulative increase of deaths adjusted for the population size of each state.

```{r cum_deaths_per100, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}

states16.final <- germany.16states[germany.16states$DeathsDays_5 > 0,]

# Plot 1 == Linear scale for total number of cases
deathper100.plot <- ggplot(data=states16.final, aes(x=DeathsDays_5, y=DeathPer100, group=State, color=State)) +
            geom_line() + geom_point(size = 0.3) + 
            # scale_color_brewer(palette = 'Paired') +
            scale_colour_manual(name= "State", values= colors16) +
            scale_x_continuous('Days since 5 deaths', limits=c(0,160)) + 
            scale_y_continuous("Cumulative deaths per 100,000") + 
            #ggtitle('Linear scale') +
            theme_minimal()

print(deathper100.plot)

```
<br/>
<br/>
<br/>

##### Number of confirmed new deaths since March 21,2020

This plot shows the increase in the number of confirmed deaths. Each data point is averaged over past 7 consecutive days. *(modified from 5-day average to 7 days on April 25,2020).* 

_**April 12, 2020**: Note: I am not sure if the decrease in deaths is real or if fewer cases and deaths are reported over the Easter long weekeend._

_**April 16, 2020**: Sure enough, the rates of reported deaths went back up on work days. However, given that the rates of deaths lag behind the rates of confirmed new cases, I expect/hope these numbers to go down for real next week._


```{r deaths_7days, echo = F, message = F, warning=F, fig.width=8, fig.height=5, dpi=96}
#new.cases <- read_csv(here("static", "data", "GermanyNewCases10States.csv"))

states.final$Dates <- as.Date(states.final$Dates)
death7days <- states.final
death7days <- death7days[death7days$Dates > as.Date('2020-03-20'),]

death7days.plot <- ggplot(data=death7days, aes(x=Dates, y=Death_7days, group=State, color=State)) +
            geom_line() + geom_point(size = 0.3) + 
       #     scale_color_brewer(palette = 'Paired') +
            scale_colour_manual(name= "State", values= colors16) +
            scale_x_date(name='Date', labels=date_format('%Y-%m-%d')) + 
            scale_y_continuous(name="Number of new deaths (averaged over 7 days)") + 
           
            #ggtitle('Linear scale') +
            theme_minimal() + theme(axis.text.x = element_text(angle=20, hjust=0.5, vjust=0.5))

print(death7days.plot)
 
```
<br/>
<br/>
<br/>






